---
title: "Coffe Chain analysis Report"
date: "11/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analyzing Public coffee chains and their models for investment.
###			Dunkin Donuts vs Starbucks

We started our coffee chain analysis research by first shortlisting top public chains who go head on.
One of them was Starbucks Corporation formed in 1985 is a seattle based coffee company who has a huge internationally brand presence. It's competitor is DUNKIN’ BRANDS GROUP, INC. , also an Internation brand made up of two companies Dunkin Donuts and Baskins and Robins selling ice cream and donuts formed in 1980s and combined in one in 2002.

1. In Order to understand this brands power of prensence in United staties lets see the state wise plot

a. Starbucks

```{r Starbuckscentroid}

```

As we concer California has highest number main reason being it's closest highly populated state next to Seattle the birth place of Starbucks

Where is the maximum density?
```{r StarbucksDesity}

```

The average density of starbucks is ___ per mile.

b. Dunkin Brand

```{r DunkinCentroidboth}

```

As we concer California has highest number main reason being it's closest highly populated state next to Seattle the birth place of Starbucks

Where is the maximum density?
```{r DunkingDensity}

```



2. Lets visual and see the stock growth.

a. Starbucks

```{r Starbucksplot, echo=FALSE}
```
The Growth rate for starbucks is __

b. Dunkin Donuts
```{r Dunkinplot, echo=FALSE}
```
The Growth rate of Dunkin is __


We can clearly  Stabucks is coming ahead as far as the growth rate is concerned. You can also see that starbucks had a stock split in 2015

3. Finally revenues and store counts is key to conclude if we should invest in

Lets investigate their business model and lets look how their profits and loss are being affected over the time.

```{r StarbucksStore, echo=FALSE}
```

```{r StarbucksRevenues, echo=FALSE}
```

Points of disruption in revenues in Starbucks?  And why? 


```{r DunkinStores, echo=FALSE}
```

```{r DunkinStoresRevenues, echo=FALSE}
```

Points of disruption in revenues in Dunkin Brand?  And why?

We can see that Dunkin changed to full franchise modle in 20__ .
We can see growth


In Conclusion 




